High Resolution Spectroscopic Analysis of Orphan Stream Giants

### 2012-07-29 2012-oss/draft-oss.tex
alpha elements in for all OSS TGTS

ALPHA ELEMENTS Mg, Si, Ca, Ti <-> (12, 
==============

@@

@@

=============
4580 K / 2.05 / 0.80 / -2.79 / +0.40
( doesn't quite sit on the expected isochrone)

@@

@@

Guessing [Fe/H] = -1.9 yields Teff = 4709 K
Arbitrarily chosing lines only redward of 4400 A

5200 / 2.0 / 2.9 / -0.95 / 0.40

@@

>>>>

ALPHA ELEMENTS Mg, Si, Ca, Ti
==============

@@

FINAL (this was done blindly too because I actually thought I was analysing OSS4)
=====
4780 / 1.7 / 1.55 / -1.79 / +0.40 <--> fits well on isochrone, saved as "FINAL"

Fe I abundance: 5.71 +/- 0.12 (154 lines)
SOC: 0.00, 5.70, 0.04 // -0.03, 5.57, -0.05 // 3.21e-05, 5.55, 0.20

Fe II abundance: 5.71 +/- 0.16 (20 lines)
SOC: // 0.03, 5.84, 0.04 // 6.42e-05, 5.39, 0.25

ALPHA ABUNDANCES Mg, Si, Ca, Ti
================

Mg I: 5.95 +/- 0.05 (5 lines), Solar 7.60 +/- 0.04
I inspected all the lines and clipped outliers.
SOC: -0.01, 5.95, -.18 // 0.11, 6.44, 0.84 // -9.34e-05, 6.40, -0.72
[Mg I/Fe] = 0.14 +/- 0.05

Si I: 6.25 +/- 0.05 (2 lines), Solar 7.51 +/- 0.03
excluded no lines:
5565 line is not present
5701 line is present, blended and not measured by code -- I measured it by hand
5772 line is not present
The two lines we have look really good.
After I measured the line at 5701 and put them in:
Si I: 6.20 +/- 0.16 (3 lines), Solar 7.51 +/- 0.03
SOC: -0.03, 6.25, -0.27 // 0.22, 7.25, 0.65 // -5.47e-05, 6.42, -0.26
[Si I/Fe] = 0.48 +/- 0.16

Ca I: 4.87 +/- 0.09 (18 lines), Solar 6.34 +/- 0.04
I inspected all the lines and clipped outliers.
SOC: // 0.15, 5.61, 0.30 // 3.62e-05, 4.66, 0.30
[Ca I/Fe] = 0.32 +/- 0.09

Ti I: 3.13 +/- 0.09 (23 lines), Solar 4.95 +/- 0.05
I inspected all the lines + clipped outliers
SOC: // -0.01, 3.10, -0.02 // -5.4e-06, 3.18, -0.02
[Ti I/Fe] = -0.03 +/- 0.09

Ti II: 3.36 +/- 0.09 (24 lines), Solar 4.95 +/- 0.05
I inspected all the lines + clipped outliers
SOC: -0.04, 3.42, -0.16 // 0.08, 3.74, 0.18 //-1.35e-05, 3.43, -0.06
[Ti II/Fe] = 0.20 +/- 0.09

Na: 4.42 +/- 0.07 (3 lines), Solar 6.24 +/- 0.04
SOC: -0.07, 4.43, -1.00 // 0.15, 5.09, 0.99
[Na I/Fe] = -0.03 +/- 0.07

@@

FINAL
=============
4580 K / 2.05 / 0.80 / -2.79 / +0.40
( doesn't quite sit on the expected isochrone)

@@

FINAL WITH EXCLUSIONS
=====================
4580 K / 2.05 / 0.80 / -2.75 / +0.40

Fe I abundance: 4.74 +/- 0.11 (89 lines)
SOC: 0.00, 4.75, -0.05 // -0.01, 4.70, -0.02 // 9.19e-06, 4.70, 0.06

Fe II abundance: 4.77 +/- 0.12 (13 lines)
SOC: // 0.00, 4.74, -0.01 // 1.16e-04, 4.21, 0.34

Saved as "FINAL" <-> adopting these values

ALPHA ELEMENTS
==============

Mg I: 5.11 +/- 0.13 (7 lines), Solar 7.60 +/- 0.04
Inspected all lines, kept good ones then removed two spurious outliers.
SOC: -0.02, 5.14, -0.19 // -0.14, 4.44, -0.31 // 1.54e-04, 4.39, 0.74
[Mg I/Fe] = 0.26 +/- 0.13

Si I: 5.38 +/- 0.03 (3 lines), Solar 7.51 +/- 0.03
Inspected all lines and removed one outlier.
SOC: -0.01, 5.43, -0.72 // 0.02, 5.50, 0.54 // -2.42e-05, 5.50,-0.65
[Si I/Fe] = 0.62 +/- 0.03

Ca I: 3.75 +/- 0.09 (9 lines), Solar 6.34 +/- 0.04
Inspected all lines as usual
SOC: // // 2.84e-05, 3.60, 0.26
[Ca I/Fe] = 0.16 +/- 0.10

Na I: 3.69 +/- 0.04 (2 lines), Solar 6.24 +/- 0.04
Inspected both lines (they were all that was measured) & they are very clean.
SOC: // // //
[Na I/Fe] = 0.20 +/- 0.04

Ti I: 2.28 +/- 0.15 (13 lines), Solar 4.95 +/- 0.05
Inspected lines as always; these lines were more difficult to measure than usual.
SOC: // 0.09, 2.70, 0.14 // -1.08e-04, 2.75, -0.24
[Ti I/Fe] = 0.08 +/- 0.15

Ti II: 2.31 +/- 0.09 (24 lines), Solar 4.95 +/- 0.05
SOC: 0.00, 2.31, -0.02 // 0.00, 2.32, 0.01 // 2.39e-05, 2.19, 0.12
[Ti II/Fe] = 0.11 +/- 0.15

Alphas saved as "ALPHA"

@@

Guessing [Fe/H] = -1.9 yields Teff = 4709 K
Arbitrarily chosing lines only redward of 4400 A because S/N shit.

5200 / 2.0 / 2.9 / -0.95 / 0.40 (fits perfectly on the isochrone)

@@

FINAL
5250 / 1.85 / 3.00 / -0.80 / 0.40 (first perfectly on isochrone)

Fe I: 6.68 +/- 0.18 (99 lines)
-0.01, 6.72, -0.06
0.00, 6.68, 0.00
5.61e-05, 6.38, 0.19

Fe II: 6.71 +/- 0.25 (14 lines)
0.28, 8.07, 0.24
5.55e-05, 6.42, 0.16

USING THESE VALUES (saved as "results")

NOTE: so because this spectra is so shitty i ignored all lines (Fe, alpha elements) blue ward of 4000 Angstroms EXCEPT for Silicon only because there are so few lines.

ALPHA ELEMENTS
==============

Mg I: 6.70 +/- 0.15 (5 lines), Solar 7.60 +/- 0.04
All inspected
SOC: -0.05, 6.94, -0.61 // -1.48e-04, 7.49, -0.58
[Mg I/Fe] = -0.10 +/- 0.15

Na I: 5.17 +/- 0.13 (4 lines), Solar 6.24 +/- 0.04
All inspected and look good.
SOC: 0.11, 5.08, 0.96 // -0.36, 3.53, -0.97 // //
[Na I/Fe] = -0.27 +/- 0.13

Si I: 6.78 +/- 0.31 (4 lines), Solar 7.51 +/- 0.03
Lines look okay, but spectrum is crappy.
SOC: 0.12, 6.35, 0.59 // -0.07, 6.41, -0.14 // 1.92e-04, 5.82, 0.54
[Si I/Fe] = 0.07 +/- 0.31

Ca I: 5.77 +/- 0.12 (10 lines), Solar 6.34 +/- 0.04
All lines inspected and look good.
SOC: // // -1.49e-04, 6.68, -0.45
[Ca I/Fe] = 0.23 +/- 0.12

Ti I: 4.26 +/- 0.36 (15 lines), Solar 4.95 +/- 0.05
Lines look good, excluded all outliers and it's still a bit crap. Lot of scatter!
SOC: // 0.95, 8.88, 0.54 // 2.20e-04, 3.25, 0.24
[Ti I/Fe] = 0.11 +/- 0.36

Ti II: 4.28 +/- 0.19 (13 lines), Solar 4.95 +/- 0.05
Lines are good; could have gotten rid of a few more outliers but chose not to.
SOC: 0.04, 4.16, 0.13 // // 7.89e-05, 3.86, 0.16
[Ti II/Fe] = 0.13 +/- 0.19
